---
title: "Homework № 1"
author: "Dian Todorov, 61670"
date: "December 9, 2015"
output: pdf_document
---

Task 1.
======
```{r}
#install.packages("faraway")
library("faraway")
data(sat)
attach(sat)
```

Task 2.
======
```{r}
#nrow(sat) -> counts the number of rows in the dataframe
#sample(nrow(sat), 35) -> emits 35 random numbers in the range of 50 and 35
#sat[sample(nrow(sat), 35), ] -> emits random 35 items from the dataframe sat
df <- data.frame(sat[sample(nrow(sat), 35), ] ) #creates the dataframe
```

Task 3.
======
3.1  Descriptive statistics
-----

```{r}
summary(df)
```

3.2 Plots
----

* expends
We divide the expends into 7 breaks and we rug them so we can examine their distribution.
```{r}
hist(expend, breaks = 7)
rug(jitter(expend))
```

* ratio
```{r}
hist(ratio)
```
* salary

After boxplotting the salaries of the teachers we see that there is an outlier. A close examination of the plot tells that there is a teacher with a bigger unusually bigger salary compared to others. By using the following we can exactly nam which one it is.

```{r}
salaryBoxplot <- boxplot(salary)
df$salary[which(df$salary %in% salaryBoxplot$out)]
row.names(df)[which(df$salary %in% salaryBoxplot$out)]
```


* takers

```{r}s
tmp = hist(takers, breaks = 10)
lines(c(min(tmp$breaks), tmp$mids,max(tmp$breaks)),c(0 ,tmp$counts,0),type="l")
```

* verbal
```{r}
hist(verbal)
```
* math
```{r}
boxplot(verbal)
```
* total
```{r}
boxplot(verbal)
```

Task 4.
======
#3

4.1 Expend to salary
The coefficient of correlation is close to 1. Thus there is an approximate linar 
```
cor(expend, salary)
```